---
title: "mtcarsShinyApp"
author: "KKher"
date: "8/28/2020"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

## Introduction

I intend by this App to show the capacity of Shiny App.

data used is mtcars dataset, it is built-in RStudio. mtcars data comes from the 1974 Motor Trend magazine. The data includes fuel consumption data, and ten aspects of car design for then-current car models.

## What User can do

- See distribution of mpg Vs. cyl per transmission type, and you can add box/violin plot
- See structure of our data and you can view its summary
- See coefficients of linear model for mpg against all vairables, and as an example, plotted mpg against wt, where you see fitted line for any selection of points you chose

## mgp Vs. cyl & am

```{r cars, echo = TRUE}
library(shiny)
data("mtcars")
library(plotly)
library(ggplot2)
mtcars$cyl <- as.factor(mtcars$cyl)
p <- ggplot(mtcars, aes(x=cyl, y=mpg, fill=am)) + 
             geom_dotplot(binaxis='y', stackdir='center',
                          stackratio=1.5, dotsize=1.2, stroke=1, 
                          position=position_dodge(0.8))
p
```

## Interactive plot:

```{r lmPlot, echo=TRUE}
g <- ggplot(mtcars, aes(x=wt,y=mpg)) + 
            labs(y = "Milage per Gallon", x = "Weight", main = "mtcars Data") +
            geom_point()
g
```

## Application:

My application can be tried and found through this [link](https://kkher.shinyapps.io/mtcarsShinyApp/?_ga=2.218082134.1740965407.1598637125-1292790713.1598637125)
